---
title: "movielibutils"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{movielibutils}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(movielibutils)
```
## Introduction

This package was created to help users fetch metadata about movies using the TMDB API.

### create_masterlist(wd, convention, api_key)

This is top-level function of this package and should be your go-to in case you need a fast way to get every detail.

**Every movie can have multiple genre_ids and production_companies. These multiply every set of rows so that there can be one master dataframe with all the data.**

The resulting dataframe looks like this. Movie details are prefixed "m_", cast and crew columns are prefixed with "cc_".

```
 [1] "results.id"
 [2] "disc_dir"
 [3] "m_adult"
 [4] "m_backdrop_path"
 [5] "m_budget"
 [6] "m_genres.id"
 [7] "m_genres.name"
 [8] "m_homepage"
 [9] "m_imdb_id"
[10] "m_original_language"
[11] "m_original_title"
[12] "m_overview"
[13] "m_popularity"
[14] "m_poster_path"
[15] "m_production_companies.id"
[16] "m_production_companies.logo_path"
[17] "m_production_companies.name"
[18] "m_production_companies.origin_country"
[19] "m_production_countries.iso_3166_1"
[20] "m_production_countries.name"
[21] "m_release_date"
[22] "m_revenue"
[23] "m_runtime"
[24] "m_spoken_languages.english_name"
[25] "m_spoken_languages.iso_639_1"
[26] "m_spoken_languages.name"
[27] "m_status"
[28] "m_tagline"
[29] "m_title"
[30] "m_video"
[31] "m_vote_average"
[32] "m_vote_count"
[33] "m_belongs_to_collection.id"
[34] "m_belongs_to_collection.name"
[35] "m_belongs_to_collection.poster_path"
[36] "m_belongs_to_collection.backdrop_path"
[37] "cc_adult"
[38] "cc_gender"
[39] "cc_id"
[40] "cc_known_for_department"
[41] "cc_name"
[42] "cc_original_name"
[43] "cc_popularity"
[44] "cc_profile_path"
[45] "cc_cast_id"
[46] "cc_character"
[47] "cc_credit_id"
[48] "cc_order"
[49] "cc_department"
[50] "cc_job"
```

### extract_names(name_vector, convention)

This function extracts metadata (title, year, opt. subtitles) according to the chosen naming convention into a dataframe and returns it. 

### id_list(title_col, year_col, id_col, api_key)

Looks up the supplied movies **TMDB ID** using the TMDB API. Supply year for more precise results - otherwise year = NULL is also ok.
The id_col parameter adds an user-supplied identifier to the returning dataframe for later joins.

If multiple matches are found for the parameters the title with the highest popularity is chosen.

```
[1] "results.id"
[2] "disc_dir"  
```

### get_genres(api_key)

This function returns a dataframe containing TMDB genre ids and their respective name.
```
[1] "genres.id"
[2] "genres.name"
```

### get_details(tmdb_id, api_key) 

Looks up the movie details for the supplied TMDB id(s). Returns the following dataframe:

```
 [1] "m_adult"
 [2] "m_backdrop_path"
 [3] "m_budget"
 [4] "m_genres.id"
 [5] "m_genres.name"
 [6] "m_homepage"
 [7] "m_id"
 [8] "m_imdb_id"
 [9] "m_original_language"
[10] "m_original_title"
[11] "m_overview"
[12] "m_popularity"
[13] "m_poster_path"
[14] "m_production_companies.id"
[15] "m_production_companies.logo_path"
[16] "m_production_companies.name"
[17] "m_production_companies.origin_country"
[18] "m_production_countries.iso_3166_1"
[19] "m_production_countries.name"
[20] "m_release_date"
[21] "m_revenue"
[22] "m_runtime"
[23] "m_spoken_languages.english_name"
[24] "m_spoken_languages.iso_639_1"
[25] "m_spoken_languages.name"
[26] "m_status"
[27] "m_tagline"
[28] "m_title"
[29] "m_video"
[30] "m_vote_average"
[31] "m_vote_count"
[32] "m_belongs_to_collection.id"
[33] "m_belongs_to_collection.name"
[34] "m_belongs_to_collection.poster_path"
[35] "m_belongs_to_collection.backdrop_path"
```

### cast_crew_list(id_col, api_key) 

Looks up the cast and crew for the supplied TMDB id(s). Returns the following dataframe:

```
[1] "cc_adult"
[2] "cc_gender"
[3] "cc_id"
[4] "cc_known_for_department"
[5] "cc_name"
[6] "cc_original_name"
[7] "cc_popularity"
[8] "cc_profile_path"
[9] "cc_cast_id"
[10] "cc_character"
[11] "cc_credit_id"
[12] "cc_order"
[13] "cc_department"
[14] "cc_job"
[15] "cc_results.id"
```

## Convention (Naming Conventions)

For extract_names() the convention parameter needs to be supplied.
Currently there four different conventions supported:

1. "1999 - The Matrix"
2. "(1999) The Matrix"
3. "The Matrix (1999)"
4. "The Matrix (1999) (OmU)"

If you use a naming convention that is reasonable and not supported yet, feel free to submit a pull request on [Github](https://github.com/tilschuenemann/movielibutils/pulls).
